19Q2

### 2019-10-29 19Q2.Rmd

g2p$biomarker_type_curated <- ifelse(is.na(g2p$biomarker_type_curated), "None", as.character(g2p$biomarker_type_curated))
g2p_split <- filter(g2p, !is.na(Drug)) %>% split(g2p$biomarker_type_curated)
g2p_amp <- g2p_split[[1]]
g2p_expr <- g2p_split[[2]]
g2p_fus <- g2p_split[[3]]
g2p_fus$FusionPair <- sapply(X = g2p_fus$Feature.Names, function(x) strsplit(as.character(x)," ")[[1]][1])
g2p_fus$FusionPair <- ifelse(g2p_fus$FusionPair == "Fusions", as.character(g2p_fus$Gene), as.character(g2p_fus$FusionPair))
g2p_fus$FusionPair <- ifelse(g2p_fus$FusionPair == "BCR-ABL", "BCR-ABL1", as.character(g2p_fus$FusionPair))
g2p_fus$Drug_FusionPair <- ifelse(is.na(g2p_fus$Drug) | is.na(g2p_fus$FusionPair), NA, paste0(g2p_fus$Drug, "_", g2p_fus$FusionPair))
g2p_fus$Drug_Fusion_Lineage <- ifelse(is.na(g2p_fus$Drug) | is.na(g2p_fus$FusionPair) | is.na(g2p_fus$disease), NA, paste0(g2p_fus$Drug, "_", g2p_fus$FusionPair, "_", g2p_fus$disease))
g2p_mut <- g2p_split[[4]] %>% drop_na(Direction_Curated)
g2p_mut_genes <- unique(sapply(strsplit(as.character(g2p_mut$Drug_Gene)[!is.na(g2p_mut$Drug_Gene)], "_", fixed = TRUE), function(x) x[2]))

@@

@@

@@

ccle_fus <- filter(fus, Database == "CCLE")
ccle_fus <- unfactorize(ccle_fus)

ctrp_fus <- filter(fus, Database == "CTRP")
ctrp_fus <- unfactorize(ctrp_fus)

gdsc_fus <- filter(fus, Drug %in% g2p_drugs & Database == "GDSC")
gdsc_fus <- unfactorize(gdsc_fus)
```

@@

@@

  print("Making heatmap object.")
  ht <- Heatmap(signif_grid,
                col = col_fun,
                na_col = na_color,
                rect_gp = gpar(col = "gray70"),
                heatmap_legend_param = ht_legend_list,
                cluster_rows = FALSE, 
                cluster_columns = FALSE, 
                show_row_names = as.logical(row_names),
                row_names_side = "left",
                row_names_gp = gpar(fontsize = 10),
                column_names_side = "bottom",
                column_names_gp = gpar(fontsize = 10),
                show_column_names = FALSE,
                bottom_annotation = HeatmapAnnotation(
                  text = anno_text(colnames(signif_grid),
                                   rot = 45,
                                   gp = gpar(fontsize = 11),
                                   offset = unit(1, "npc"),
                                   just = "right"),
                  annotation_height = unit(0.85, "in")),
                  # annotation_height = max_text_width(colnames(signif_grid))),
                row_title = row_title_txt,
                row_title_gp = gpar(fontface = "bold", fontsize = 14),
                column_title = col_title, 
                column_title_gp = gpar(fontface = "bold", fontsize = 14),
                column_title_side = "bottom",
                cell_fun = function(j, i, x, y, width, height, fill) {
                  if(color == "darkorchid4") {
                    if(is.na(str_match(string = tolower(feature), pattern = "prot"))) { radius <- height*3.3 }
                    if(!is.na(str_match(string = tolower(feature), pattern = "prot"))) { radius <- height*2 }
                  }
                  if(color == "steelblue4") {
                    if(!is.na(str_match(string = tolower(feature), pattern = "fus"))) { radius <- height*0.20 }
                    if(!is.na(str_match(string = tolower(feature), pattern = "prot"))) { radius <- height*0.16 }
                    else { radius <- width*0.18 }
                  }
                  if(color == "darkgreen") {
                    if(!is.na(str_match(string = tolower(feature), pattern = "fus"))) { radius <- height*0.16 }
                    if(!is.na(str_match(string = tolower(feature), pattern = "prot"))) { radius <- height*0.3 }
                    else { radius <- width*0.17 }
                  }
                  if(color == "turquoise4") {
                    if(!is.na(str_match(string = tolower(feature), pattern = "fus|prot"))) { radius <- height*0.16 }
                    else { radius <- width*0.18 }
                  }

@@

  print("Done.")
  return(ht)
}
```

>>>>

g2p$biomarker_type_curated <- ifelse(is.na(g2p$biomarker_type_curated), "None", as.character(g2p$biomarker_type_curated))
g2p_split <- filter(g2p, !is.na(Drug)) %>% split(g2p$biomarker_type_curated)
g2p_amp <- g2p_split[[1]]
g2p_expr <- g2p_split[[2]]
g2p_fus <- g2p_split[[3]]
g2p_fus$FusionPair <- sapply(X = g2p_fus$Feature.Names, function(x) strsplit(as.character(x)," ")[[1]][1])
g2p_fus$FusionPair <- ifelse(g2p_fus$FusionPair == "Fusions", as.character(g2p_fus$Gene), as.character(g2p_fus$FusionPair))
g2p_fus$FusionPair <- ifelse(g2p_fus$FusionPair == "BCR-ABL", "BCR-ABL1", as.character(g2p_fus$FusionPair))
g2p_fus <- g2p_fus[grep("-", g2p_fus$FusionPair), ]
g2p_fus$Drug_FusionPair <- ifelse(is.na(g2p_fus$Drug) | is.na(g2p_fus$FusionPair), NA, paste0(g2p_fus$Drug, "_", g2p_fus$FusionPair))
g2p_fus$Drug_Fusion_Lineage <- ifelse(is.na(g2p_fus$Drug) | is.na(g2p_fus$FusionPair) | is.na(g2p_fus$disease), NA, paste0(g2p_fus$Drug, "_", g2p_fus$FusionPair, "_", g2p_fus$disease))
g2p_mut <- g2p_split[[4]] %>% drop_na(Direction_Curated)
g2p_mut_genes <- unique(sapply(strsplit(as.character(g2p_mut$Drug_Gene)[!is.na(g2p_mut$Drug_Gene)], "_", fixed = TRUE), function(x) x[2]))

@@

```{r}
ccle_signif_dgl %>% count(InG2P)
filter(ccle_signif_dgl, InG2P == "Yes" & p < 0.05) %>% select(Drug, Gene, disease, p.short, Direction_Heatmap)
ctrp_signif_dgl %>% count(InG2P)
filter(ctrp_signif_dgl, InG2P == "Yes" & p < 0.05) %>% select(Drug, Gene, disease, p.short, Direction_Heatmap)
gdsc_signif_dgl %>% count(InG2P)
filter(gdsc_signif_dgl, InG2P == "Yes" & p < 0.05) %>% select(Drug, Gene, disease, p.short, Direction_Heatmap)
```

@@

```{r}
all_directions <- readRDS("./data_munging/rds/protein_changes_directions.rds")
crispr_signif_prot_lin <- readRDS("./data_munging/rds/crispr_signif_protein_changes_lineage.rds")
crispr_signif_prot_lin <- merge(crispr_signif_prot_lin, all_directions, by = c("Gene_Protein_Change", "Drug"), all.x = TRUE)
ccle_signif_prot_lin <- readRDS("./data_munging/rds/ccle_signif_protein_changes_lineage.rds")
ccle_signif_prot_lin <- merge(ccle_signif_prot_lin, all_directions, by = c("Gene_Protein_Change", "Drug"), all.x = TRUE)
ctrp_signif_prot_lin <- readRDS("./data_munging/rds/ctrp_signif_protein_changes_lineage.rds")
ctrp_signif_prot_lin <- merge(ctrp_signif_prot_lin, all_directions, by = c("Gene_Protein_Change", "Drug"), all.x = TRUE)
gdsc_signif_prot_lin <- readRDS("./data_munging/rds/gdsc_signif_protein_changes_lineage.rds")
gdsc_signif_prot_lin <- merge(gdsc_signif_prot_lin, all_directions, by = c("Gene_Protein_Change", "Drug"), all.x = TRUE)

ccle_signif_prot_lin %>% count(InG2P)
filter(ccle_signif_prot_lin, InG2P == "Yes" & p < 0.05) %>% select(Drug, Gene_Protein_Change, disease, p.short, Direction_Curated)
ctrp_signif_prot_lin %>% count(InG2P)
filter(ctrp_signif_prot_lin, InG2P == "Yes" & p < 0.05) %>% select(Drug, Gene_Protein_Change, disease, p.short, Direction_Curated)
gdsc_signif_prot_lin %>% count(InG2P)
filter(gdsc_signif_prot_lin, InG2P == "Yes" & p < 0.05) %>% select(Drug, Gene_Protein_Change, disease, p.short, Direction_Curated)
```

@@

ccle_fus <- filter(fus, Database == "CCLE")
ccle_fus <- unfactorize(ccle_fus)
# ccle_fus_summ <- unique(select(ccle_fus, DepMap_ID, FusionPair, Fusion_Status)) %>% count(FusionPair, Fusion_Status)

ctrp_fus <- filter(fus, Database == "CTRP")
ctrp_fus <- unfactorize(ctrp_fus)
# ctrp_fus_summ <- unique(select(ctrp_fus, DepMap_ID, FusionPair, Fusion_Status)) %>% count(FusionPair, Fusion_Status)

gdsc_fus <- filter(fus, Drug %in% g2p_drugs & Database == "GDSC")
gdsc_fus <- unfactorize(gdsc_fus)
# gdsc_fus_summ <- unique(select(gdsc_fus, DepMap_ID, FusionPair, Fusion_Status)) %>% count(FusionPair, Fusion_Status)
```

@@

**10/29 NEED TO FIX CIRCLE ANNOTS ON FUSION/STEELBLUE4 HEATMAP**

@@

  print("Making heatmap object.")
  ht <- Heatmap(signif_grid,
                col = col_fun,
                na_col = na_color,
                rect_gp = gpar(col = "gray70"),
                heatmap_legend_param = ht_legend_list,
                cluster_rows = FALSE, 
                cluster_columns = FALSE, 
                show_row_names = as.logical(row_names),
                row_names_side = "left",
                row_names_gp = gpar(fontsize = 10),
                column_names_side = "bottom",
                column_names_gp = gpar(fontsize = 10),
                show_column_names = FALSE,
                bottom_annotation = HeatmapAnnotation(
                  text = anno_text(colnames(signif_grid),
                                   rot = 45,
                                   gp = gpar(fontsize = 11),
                                   offset = unit(1, "npc"),
                                   just = "right"),
                  annotation_height = unit(0.85, "in")),
                row_title = row_title_txt,
                row_title_gp = gpar(fontface = "bold", fontsize = 14),
                column_title = col_title, 
                column_title_gp = gpar(fontface = "bold", fontsize = 14),
                column_title_side = "bottom",
                cell_fun = function(j, i, x, y, width, height, fill) {
                  if(color == "darkgreen") {
                    if(!is.na(str_match(string = tolower(feature), pattern = "fus"))) { radius <- height*0.16 }
                    if(!is.na(str_match(string = tolower(feature), pattern = "prot"))) { radius <- height*0.3 }
                    else { radius <- width*0.17 }
                  }
                  if(color == "steelblue4") {
                    if(!is.na(str_match(string = tolower(feature), pattern = "fus"))) { radius <- height*0.5 }
                    if(!is.na(str_match(string = tolower(feature), pattern = "prot"))) { radius <- height*0.16 }
                    else { radius <- width*0.18 }
                  }
                  if(color == "turquoise4") {
                    if(!is.na(str_match(string = tolower(feature), pattern = "fus|prot"))) { radius <- height*0.16 }
                    else { radius <- width*0.18 }
                  }
                  if(color == "darkorchid4") {
                    if(is.na(str_match(string = tolower(feature), pattern = "prot"))) { radius <- height*3.3 }
                    if(!is.na(str_match(string = tolower(feature), pattern = "prot"))) { radius <- height*2 }
                  }

@@

  print("Done.")
  return(ht)
}

# ht_ctrp <- MakeWilcoxonHeatmap(signif_df = filter(ctrp_signif_fus, Drug %in% g2p_drugs), feature = "fusion", legend_title = "-log10(p-value)", legend_breaks = seq(0, 10, by = 2), row_names = TRUE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Fusion Pairs")
# png(filename = "./plots/manuscript/ctrp_fus_heatmap.png", width = 13, height = 3, units = "in", res = 500)
# draw(ht_ctrp, heatmap_legend_side = "top")
# dev.off()
# 
# ht_ctrp <- MakeWilcoxonHeatmap(signif_df = ctrp_signif_prot_4plot, feature = "protein changes", legend_title = "-log10(p-value)", legend_breaks = seq(0, 15, by = 3), row_names = TRUE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Gene:Protein Change")
# png(filename = "./plots/manuscript/ctrp_prot_heatmap.png", width = 9.5, height = 5.5, units = "in", res = 500)
# draw(ht_ctrp, heatmap_legend_side = "top")
# dev.off()
```
